Data Management for LSST Special Programs

### 2024-03-27 sec_sci.tex
fix typo

\textbf{Caveat I. The definition of possible} comes from the requirement referenced
for the first motivation in the list above (i.e., is not defined by this document).
However, this definition failed to recognize cost-benefit tradeoffs to implementing
and operating Special Processing, and does not account for the costs of operating,
documenting, and maintaining additional processing campaigns and their data products.
Even in situations that require no algorithmic or software development,
the Rubin DM team might not have the staffing to handle Special Processing
for all cases that are technically "possible".
Current ballpark estimates are that the DM effort for Special Processing
should be commeasurate with the 10\% level estimated for survey time,
storage space, and computational resources allocated for Special Programs.

>>>>

\textbf{Caveat I. The definition of possible} comes from the requirement referenced
for the first motivation in the list above (i.e., is not defined by this document).
However, this definition failed to recognize cost-benefit tradeoffs to implementing
and operating Special Processing, and does not account for the costs of operating,
documenting, and maintaining additional processing campaigns and their data products.
Even in situations that require no algorithmic or software development,
the Rubin DM team might not have the staffing to handle Special Processing
for all cases that are technically "possible".
Current ballpark estimates are that the DM effort for Special Processing
should be commensurate with the 10\% level estimated for survey time,
storage space, and computational resources allocated for Special Programs.
